%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

%\begin{flushright}{\slshape    
%    Charity given to a worthy person\\
%    simply because it is right to give,\\
%    without consideration of anything in return,\\
%    at the proper time and in the proper place,\\
%     is stated to be in the mode of goodness.} \\ \medskip
%    --- \defcitealias{Bhagvad Gita:17.20}{Donald E. Knuth}\citetalias{Bhagvad Gita:17.20}
%\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
I would like to extend my sincere thanks to my primary supervisor and mentor Professor
Peter Xu, who has the substance of a genius: he convincingly guided and encouraged me throughout my PhD research journey and do the right thing even when the road got tough. Without his thoughtful encouragement and careful supervision, the thesis would have never taken shape. His unwavering enthusiasm and motivation during our fruitful discussions, kept me constantly engaged during our research. He has furnished me with motivation to explore many new research, and academic, opportunities and has been my most reliable promoter. 

%I am grateful for the freedom with which he let us investigate, while guaranteeing we advanced down this path less meandered.

I would also like to express my thanks to my co-supervisor, Prof. Leo K.
Cheng, who has provided a lot of relevant and insightful thoughts for this study. Through our regular discussions, he conveyed to me his interdisciplinary knowledge of bio-medical science, mechatronics engineering, and biological modelling, which equipped me to unearthed several innovative ideas to achieve the goals of this research. 

I would line to show my deep gratitude to the technical assistance of Emanuele Romalo, Marshall Lim, and Logan Stuart for their plentiful time in manufacturing and procuring components
on my behalf. The domain knowledge, and craftsmanship, they have shown have always been outstanding. I wish to thank my fellow PhD students, Abdul Sattar, Ryman Hashem, Sherine Jesna, and Yu Dang, whose assistance was a milestone in completion of this research.

I would also like to acknowledge the financial assistance and support provided by the University of Auckland and the Riddet Institute for the journey of this research. I am proud to endorse their
brands and share with them the published academic outcomes.

I am indebted to the endless support and great love of my father, Tapan; my mother, Aparna; my brother Chinmoy; and my sister, Poushalli. Their motivation, and encouragement kept me going on, and made this journey short, joyful and accompanied. Finally, I acknowledge, my wife Sushma, who is my champion and who blessed me with a life of joy in the hours of despair and apathetic. 


\endgroup



